The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2018-07-26 Paper/jaccardbaetica.tex
correct fig lines
add new graphic

We studied a dataset of 3798 stamps collected from different Dressel 20 amphora workshops in Baetica province. The stamp database was compiled by CEIPAC database \citep{remesal_centro_2015} (see CEIPAC database here \url{http://romanopendata.eu}). However, approximately the 70 \% of stamps cannot be tested due to fragmentation or incomplete information. Consequently, we discard integrate the fragmented stamps in our dataset. We finally filter a total sample of 987 stamps comprised of 130 different stamps from 81 workshops.

@@

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/frequency}
\caption{Distribution of the number of stamps for each area. Colors are represented by areas divided into Hispalis (red), Astigi (green) and Corduba (blue).}
\label{frequency}
\end{figure}

\xavi{gráfico molón, y útil; haría los puntos y letras de los ejes más gordos solo}

\xavi{entiendo que són códigos, no sellos? Estaría bien también mostrar cuántos sellos se encuentran por yacimiento.}
%explicar por qué: mayor intensifación en las excavaciones quizás en sevilla

>>>>

We studied a dataset of 3798 stamps collected from different Dressel 20 amphora workshops in Baetica province. The stamp database was compiled by CEIPAC database \citep{remesal_centro_2015} (see CEIPAC database here \url{http://romanopendata.eu}). However, approximately the 70 \% of stamps cannot be tested due to fragmentation or incomplete information. Consequently, we discard integrate the fragmented stamps in our dataset. We finally filter a total sample of 987 stamps comprised of 130 different stamps from 81 workshops. The frequency of stamps per workshop can be seen in Fig. \ref{stamps}. Most stamps are distributed in only one workshop whereas few workshops concentrate a high frequency of different amphoric stamps.

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/frequencystamp.pdf}
\caption{Distribution of the number of stamps}
\label{stamps}
\end{figure}

@@

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/frequency}
\caption{Distribution of the number of different code stamps for each area. Colors are represented by areas divided into Hispalis (red), Astigi (green) and Corduba (blue).}
\label{frequency}
\end{figure}

%\xavi{gráfico molón, y útil; haría los puntos y letras de los ejes más gordos solo}

%\xavi{entiendo que són códigos, no sellos? Estaría bien también mostrar cuántos sellos se encuentran por yacimiento.}
%explicar por qué: mayor intensifación en las excavaciones quizás en sevilla
